Wetting of the tarsal adhesive fluid controls underwater adhesion in ladybug beetles: Supplementary information

### 2021-08-03 source/jeb_tex/supplementary.tex
Linear mixed model results included in supplementary info.
Reviewer 1 and 3 responded and changes made in MS.
Reviewer 2 typo suggestions included

\documentclass[english]{achemso}
\setkeys{acs}{keywords = true, email=false}
\usepackage[T2A,LGR,T1]{fontenc}
\usepackage{babel}
\usepackage{array}
\usepackage{textcomp}
\usepackage{url}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subscript}
%\usepackage[unicode=true,pdfusetitle,
% bookmarks=true,bookmarksnumbered=false,bookmarksopen=false,
% breaklinks=false,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=false]
% {hyperref}
%\usepackage{lineno}
%\linenumbers

@@

The surface chemistry of untreated glass (hydrophilic) and PFOTS-coated glass (hydrophobic) were characterized using dynamic contact angle measurements (Table \ref{tab:Contact-Angles}).
\begin{table}[H]
\centering{}%
\begin{tabular}{|c|c|c|c|}
\hline 
Substrate & Liquid & \ensuremath{\theta}\textsubscript{A} & \ensuremath{\theta}\textsubscript{R}\tabularnewline
\hline 
\hline 
\multirow{2}{*}{Glass} & Water & 63\ensuremath{\pm}5\textdegree{} & 20\ensuremath{\pm}2\textdegree{}\tabularnewline
\cline{2-4} \cline{3-4} \cline{4-4} 
 & n-Hexadecane & <10\textdegree{} & <10\textdegree{}\tabularnewline
\hline 
\multirow{2}{*}{PFOTS} & Water & 122\ensuremath{\pm}1\textdegree{} & 93\ensuremath{\pm}2\textdegree{}\tabularnewline
\cline{2-4} \cline{3-4} \cline{4-4} 
 & n-Hexadecane & 88\ensuremath{\pm}2\textdegree{} & 56\ensuremath{\pm}5\textdegree{}\tabularnewline
\hline 
\end{tabular}\caption{Dynamic contact angles (Mean \ensuremath{\pm} SD, n = 3) of Milli-Q water and n-hexadecane on the different test substrates. \label{tab:Contact-Angles}}
\end{table}

@@

@@

Capillary force of a single air bubble against a PFOTS-coated glass surface are compared
for two different volumes (Figure \ref{fig:Bubble_capillary_force}). The volumes correspond to the expected
range for the case of the trapped air bubble in a ladybug's pad. Here, the bubble
was pinned to a micropatterned PDMS substrate on the top. Approach-retract tests were performed
at 62.5 \textmu m s\protect\textsuperscript{-1} speed. The maximum
adhesion force of any of the bubble never exceeds 50 \textmu N,
significantly lower than the beetle's underwater adhesion to the same
substrate (> 400 \textmu N). Thus, the bubble's contribution
to adhesion in the ``\emph{underwater: bubble}'' contact of a ladybug's
pad should be negligible. Example measurement video is included in the supplementary data (Movie3).

@@

>>>>

\documentclass[english]{achemso}
\setkeys{acs}{keywords = true, email=false}
\usepackage[T2A,LGR,T1]{fontenc}
\usepackage{babel}
\usepackage{array}
\usepackage{textcomp}
\usepackage{url}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subscript}
%\usepackage[bottom]{footmisc}
%\usepackage[unicode=true,pdfusetitle,
% bookmarks=true,bookmarksnumbered=false,bookmarksopen=false,
% breaklinks=false,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=false]
% {hyperref}
%\usepackage{lineno}
%\linenumbers

@@

The surface chemistry of untreated glass (hydrophilic) and PFOTS-coated glass (hydrophobic) was characterized using dynamic contact angle measurements (Table \ref{tab:Contact-Angles}).
\begin{table}[H]
\centering{}%
\begin{tabular}{|c|c|c|c|}
\hline 
Substrate & Liquid & \ensuremath{\theta}\textsubscript{A} & \ensuremath{\theta}\textsubscript{R}\tabularnewline
\hline 
\hline 
\multirow{2}{*}{Glass} & Water & 63\ensuremath{\pm}5\textdegree{} & 20\ensuremath{\pm}2\textdegree{}\tabularnewline
\cline{2-4} \cline{3-4} \cline{4-4} 
 & n-Hexadecane & <10\textdegree{} & <10\textdegree{}\tabularnewline
\hline 
\multirow{2}{*}{PFOTS} & Water & 122\ensuremath{\pm}1\textdegree{} & 93\ensuremath{\pm}2\textdegree{}\tabularnewline
\cline{2-4} \cline{3-4} \cline{4-4} 
 & n-Hexadecane & 88\ensuremath{\pm}2\textdegree{} & 56\ensuremath{\pm}5\textdegree{}\tabularnewline
\hline 
\end{tabular}\caption{Dynamic contact angles (Mean \ensuremath{\pm} SD, n = 3) of Milli-Q water and n-hexadecane on the different test substrates. \label{tab:Contact-Angles}}
\end{table}

@@

The effect of substrate, contact mode, tilt angle, beetle identity and repetition number on the adhesion were analysed using a linear mixed-effect model (LMEM) in Python. Here, each experimental data point was considered distinctly without averaging the repeats as before. Substrate, contact mode, tilt angle and repetition number were taken as fixed-effects, while, beetle identity was considered as the random-effect. Interaction between each of the fixed-effects were fitted using the random intercept model. Adhesion measurement on hydrophilic glass \emph{in air} was taken as the reference. The resultant fixed-effects coefficient estimates, standard error, z-statistic and p-value are reported below (Table \ref{tab:LMEM-analysis}). The random-effect (beetle identity) showed an intercept standard deviation of 100.563 \textmu N (std. error = 109.771)

\begin{table}[]
\begin{tabular}{|c|l|l|l|l|}
\hline
\multicolumn{1}{|l|}{}           & \multicolumn{1}{c|}{\textbf{Estimate}} & \multicolumn{1}{c|}{\textbf{Std. Error}} & \multicolumn{1}{c|}{\textbf{z}} & \multicolumn{1}{c|}{\textbf{p-value}} \\ \hline \hline
\textbf{Intercept \footnotemark[1]}               & 582.072                                & 170.307                                  & 3.418                           & 0.001                                 \\ \hline
\textbf{PFOTS}                   & -110.642                               & 206.268                                  & -0.536                          & 0.592                                 \\ \hline
\textbf{Underwater:   bubble}    & -304.667                               & 89.458                                   & -3.406                          & 0.001                                 \\ \hline
\textbf{Underwater: no   bubble} & -254.924                               & 117.386                                  & -2.172                          & 0.03                                  \\ \hline
\textbf{Repetition   number}     & 7.723                                  & 6.703                                    & 1.152                           & 0.249                                 \\ \hline
\textbf{Tilt angle}              & -5.649                                 & 7.088                                    & -0.797                          & 0.425                                 \\ \hline
\end{tabular}
\caption{Linear mixed-effect model statistics\label{tab:LMEM-analysis}}
\end{table}

@@

\footnotetext[1]{Adhesion on glass \emph{in air}}

Capillary force of a single air bubble against a PFOTS-coated glass surface are compared
for two different volumes (Figure \ref{fig:Bubble_capillary_force}). The volumes correspond to the expected
range for the case of the trapped air bubble in a ladybug's pad. Here, the bubble
was pinned to a micropatterned PDMS substrate on the top. Approach-retract tests were performed
at 62.5 \textmu m s\protect\textsuperscript{-1} speed. The maximum
adhesion force of any of the bubbles never exceeds 50 \textmu N,
significantly lower than the beetle's underwater adhesion to the same
substrate (> 400 \textmu N). Thus, the bubble's contribution
to adhesion in the ``\emph{underwater: bubble}'' contact of a ladybug's
pad should be negligible. Example measurement video is included in the supplementary data (Movie3).

@@

\section{Capillary bridge model: Sensitivity analysis}

Sensitivity analysis was performed using the one-at-a-time (OAT) method. Dimensionless model parameters were initially set to correspond to the ladybug's case, as given by,
contact area fraction ($\alpha=ND_{h}^{2}/D_{p}^{2}=0.1$), pad to hair diameter ratio ($D_p/D_h=50$), hair aspect ratio ($L/D_{h}=10$), water surface tension ratio ($\gamma_{wa}/\gamma_{fa}=3$),
tarsal fluid-water interfacial tension ratio ($\gamma_{fw}/\gamma_{fa}=2$), tarsal fluid size parameter ($\phi_{f}=2$), bubble size parameter ($\phi_{b}=1.6$). Substrate contact angles were kept fixed (same as in main text). Each parameter was varied within a particular range, one at a time, and the corresponding adhesion forces \emph{in air} (F\textsubscript{a}),   \emph{underwater: no bubble} (F\textsubscript{w}) and \emph{underwater: bubble} (F\textsubscript{b}) were calculated. Linear least square regression was performed to quantify the relative change in adhesion for each contact mode with respect to the varied parameter. Here, F\textsubscript{w}/F\textsubscript{a} and F\textsubscript{b}/F\textsubscript{a} were taken to be the model output. Slope and R\textsuperscript{2} values for each case are reported below (Table \ref{tab:Sens-anal}). Slope with absolute values greater than 0.5 are highlighted in bold.

\begin{table}[H]
\begin{tabular}{|l|l|l|l|l|l|l|}
\hline
\multirow{2}{*}{\textbf{Parameter}} & \multirow{2}{*}{\textbf{Range}} & \multicolumn{1}{c|}{\multirow{2}{*}{\textbf{Substrate}}} & \multicolumn{2}{c|}{\textbf{F\textsubscript{w}/F\textsubscript{a}}}                                    & \multicolumn{2}{c|}{\textbf{F\textsubscript{b}/F\textsubscript{a}}}                                    \\ \cline{4-7} 
                                    &                                 & \multicolumn{1}{c|}{}                                    & \multicolumn{1}{c|}{\textbf{slope}} & \multicolumn{1}{c|}{\textbf{R\textsuperscript{2}}} & \multicolumn{1}{c|}{\textbf{slope}} & \multicolumn{1}{c|}{\textbf{R\textsuperscript{2}}} \\ \hline  \hline
\multirow{2}{*}{$\alpha$}              & \multirow{2}{*}{0.05 - 0.3}      & Hydrophilic                                              & 3.03E-18                                  & 1.52E-03                               & 2.30E-01                                  & 7.72E-01                               \\ \cline{3-7} 
                                    &                                 & Hydrophobic                                              & -9.69E-17                                 & 3.03E-03                               &\textbf{ -9.40E-01}                                 & 7.72E-01                               \\ \hline
\multirow{2}{*}{$D_p/D_h$}             & \multirow{2}{*}{30.0 - 60.0}     & Hydrophilic                                              & -8.83E-20                                 & 1.48E-01                               & 1.28E-02                                  & 9.73E-01                               \\ \cline{3-7} 
                                    &                                 & Hydrophobic                                              & -5.65E-18                                 & 1.48E-01                               & -1.51E-02                                 & 9.82E-01                               \\ \hline
\multirow{2}{*}{$L/D_{h}$}         & \multirow{2}{*}{8.0 - 15.0}      & Hydrophilic                                              & 0.00E+00                                  & 0.00E+00                               & -5.27E-02                                 & 9.11E-01                               \\ \cline{3-7} 
                                    &                                 & Hydrophobic                                              & 0.00E+00                                  & 0.00E+00                               & 5.41E-02                                  & 8.66E-01                               \\ \hline
\multirow{2}{*}{$\gamma_{wa}/\gamma_{fa}$}              & \multirow{2}{*}{2.5 - 3.5}       & Hydrophilic                                              & -2.01E-01                                 & 8.57E-01                               & -2.43E-01                                 & 9.43E-01                               \\ \cline{3-7} 
                                    &                                 & Hydrophobic                                              & 4.11E-02                                  & 1.00E+00                               & 6.87E-02                                  & 1.00E+00                               \\ \hline
\multirow{2}{*}{$\gamma_{fw}/\gamma_{fa}$}              & \multirow{2}{*}{1.5 - 2.5}       & Hydrophilic                                              & 2.01E-01                                  & 8.62E-01                               & 1.90E-01                                  & 8.94E-01                               \\ \cline{3-7} 
                                    &                                 & Hydrophobic                                              & \textbf{5.56E-01}                                  & 1.00E+00                               & 1.57E-01                                  & 1.00E+00                               \\ \hline
\multirow{2}{*}{$\phi_{f}$}             & \multirow{2}{*}{1.7 - 2.2}       & Hydrophilic                                              & 1.29E-02                                  & 4.52E-01                               & 6.18E-02                                  & 7.94E-02                               \\ \cline{3-7} 
                                    &                                 & Hydrophobic                                              & 7.67E-02                                  & 9.84E-01                               & -3.06E-01                                 & 9.66E-01                               \\ \hline
\multirow{2}{*}{$\phi_{b}$}             & \multirow{2}{*}{1.2 - 1.8}       & Hydrophilic                                              & 0.00E+00                                  & 0.00E+00                               & \textbf{-1.14E+00}                                 & 8.85E-01                               \\ \cline{3-7} 
                                    &                                 & Hydrophobic                                              & 0.00E+00                                  & 0.00E+00                               & \textbf{1.46E+00}                                  & 9.78E-01                               \\ \hline
\end{tabular}
\caption{Sensitivity analysis \label{tab:Sens-anal}}
\end{table}
